\cvsection{Experience}

\cvevent{Co-Founder \& CTO}{\href{https://www.nommas.com}{Nommas.ai}}{Oct-2020-Present}{Riyadh,Saudi~Arabia}
\verbose{ % breif
      Co-Founded \textbf{Nommas}: a computer vision startup providing plug-n-play quality inspection for manufacturing. \\
      Managed team to build first \textbf{MVP} from scratch - containing hardware and software. Lead major \textbf{design decisions}.
      \textbf{Hired and trained} new engineers; Setup \textbf{IT infrastructure}; Ensured system \textbf{robustness}.
}{ % verbose
      Co-Founded \textbf{Nommas}: a computer vision startup providing plug-n-play quality inspection for manufacturing. \\
      \begin{itemize}
            \item Lead team to design, build and deploy first \textbf{MVP} from scratch (within 3 months) containing hardware and software.
            \item Made major \textbf{design decisions} such as hardware, model architectures, classification and model optimization/quantization methods.
            \item Ensured system \textbf{robustness}, predicted issues and developed fail-safes and backup systems.
            \item Participated in business aspects such as \textbf{pitching} and prioratizing cost-effective projects.
            \item Setup \textbf{IT infrastructure} such as, cloud platforms, update system, version control, documentation, web-hosting.
            \item \textbf{Hired and trained} new engineers.
            \item Traveled to clients to oversee product deployment as well as verifying \textbf{requirements}.
      \end{itemize}
}

\kern-0.5em \divider

\cvevent{Computer Vision \& Deep Learning Researcher}{\textit{Confidential govornment entity} under the Royal Court through BAE Systems}{2020-Present}{Riyadh,Saudi~Arabia}
\verbose{ % breif
      \textbf{Applied research in computer vision and deep learning} \\
      Pushed state-of-the-art deep learning and computer vision techniques to get increased performance on specialized tasks. Influenced and evaluated decisions costing 6~figures~\$. Directly interviewd researchers and supervised new recruits.
}{ % verbose
      \textbf{Applied research in computer vision and deep learning} \\
      \begin{itemize}
            \item Worked on pushing state-of-the-art techniques even further for specialized tasks (eg. trading accuracy with inference time).
                  Ensured applicability and feasability to work within constraints (ie. scalability, and available data). \\
            \item Evaluated, compared systems to choose which best suits \textbf{client requirements}.
            \item Directly technically interviewed over 10 research candidates.
            \item \textbf{Supervised, lead, and trained} new recruits.
            \item \textbf{Negotiated} deals and provided consultation on collaborating and participated in decisions costing over 6~figures~\$ such as research collaborations as well as purchasing hardware.
            \item Improved workflow and efficiency by pushing for new methods/systesms/workflows. Also finalizing stail decisions.
      \end{itemize}
}

\kern-0.5em \divider

% \cvevent{Freelance Game Developer}{}{\kern-0.5em Summer~of~2018}{Riyadh,Saudi~Arabia}

% \kern-1.2em \divider
\verbose{
      \cvevent{Roboticist in Computer Vision (intern)}{National Center for Robotics Technology and Autonomous Systems - King~Abdulaziz~City~for~Science~and~Technology (KACST)}{June~-~August~2019}{Riyadh,Saudi~Arabia}
      \verbose{ % brief
            Developed \textbf{computer vision algorithms}, submitted a \textbf{research paper} about computer vision, delivered multiple \textbf{project workshops} to KACST faculty and center director.
      }{ % verbose
            \begin{itemize}
                  \item Implemented basic \textbf{computer vision algorithms:} object tracking, segmentation.
                  \item Submitted a \textbf{research paper} about computer vision.
                  \item Prepared and delivered multiple \textbf{project workshops} to KACST faculty and center director.
                  % \item Filed a patent for pest control using robotics.
                  \item Worked in an interdisciplinary project and communicated technical ideas with experts in different fields.
                  % \item Read research papers, performed experiments, tested and optimized algorithms.
            \end{itemize}
      }
}{
      \cvevent{Teaching Assistant (Part-time)}{KFUPM~College~of~Computer~Science~\&~Engineering}{2017}{Dhahran,Saudi~Arabia}
}
% \kern-1.2em \divider

% \cvevent{Desk Receptionist (Summer job)}{National center of allergy, Asthma and immunology (\href{http://allergyarabia.com}{allergyarabia.com})}{Summer~of~2013}{Riyadh,Saudi~Arabia}
% Organized documents, booked \& checked-in appointments, and welcomed patients.

