% %
% % here we're starting the next sidebar (refs section)
% \cvsection[page2sidebar.tex]{}
% \clearpage \cvsection[sections/referees.tex]{}
% %

\cvsection{Projects}

% X Capstone
\cvproject{Digitized~attendance~system using face recognition}{
    \verbose{
        Take attendance of students/employees nonobtrusively with facial recognition. Proposed to fight against Coronavirus.
    }{
        A service for companies and universities to take attendance using facial recognition built on cloud and edge computing.
        This was proposed to fight against Coronavirus.
    } \small{[Group~project]}\\
}{}
\smallskip \kern-1em \divider \kern-0.5em

\cvproject{Object tracking using blob detection}{
    \verbose{}{
        Built an object tracking algorithm from scratch. \small{[Group~project]}\\
    }
}{}
\smallskip \kern-1em \divider \kern-0.5em


%% PAGE2SIDEBAR: this may need to be moved
\verbose{}{\newpage\cvsection[page2sidebar.tex]{}}
%

\cvproject{Unity Network Simulator (Packet Tracer)}{
    \verbose{}{
        A graphical simulator for computer network traffic flow. \small{[Solo~project]}\\
    }
}{FarisHijazi/UnityNetworkPacketTracer}
\smallskip \kern-1em \divider \kern-0.5em

\cvproject{Differntially-Private KMeans clustering}{
    \verbose{}{
        Implemented a differentially-private KMeans, and visualized high-dimensional data (8D) \small{[Solo~project]}\\
    }
}{FarisHijazi/PrivacyEnhancingTechnologies-projects}
\smallskip \kern-1em \divider \kern-0.5em

\cvproject{Face Generation DCGAN PyTorch}{
    \verbose{}{Built a GAN (Generative Adverserial Networks) to generate faces. \small{[Course~solo~project]}}\\
}{FarisHijazi/Face-Generation-GAN}
\smallskip \kern-1em \divider \kern-0.5em

\cvproject{LZ4 Decompressor Hardware Implementation (Verilog)}{
    \verbose{}{Designed and synthesized an LZ4 decompressor in FPGA hardware using Verilog HDL. \small{[Course~team~project]}}
}{FarisHijazi/LZ4-Decompressor-Verilog}
\smallskip \kern-1em \divider \kern-0.5em

\cvproject{Google Images enhancer (browser add-on)}{
    \verbose{}{A browser add-on that enhances the Google.com images page. Brings back ``view~image" button, adds ``download" button, and allows downloading all the full-resolution images on that page. \small{[Solo~project]}}\\
}{FarisHijazi/SuperGoogle}

\verbose{}{
    \smallskip \kern-1em \divider \kern-0.5em

    \cvproject{CPU design - single core 5-stage pipeline}{
        \verbose{}{(Course team project) Designed and simulated a functional pipelined CPU (on Logisim software) that can execute instructions. \small{[Course~team~project]}}\\
    }{}
    \smallskip \kern-1em \divider \kern-0.5em

    \cvproject{Websitenhancer (auto-CAPTCHA) (browser add-on)}{ \cvproject{Websit0.5nh
        \verbose{}{A browser add-on that adds features to a website (rarbg.to) such as auto-CAPTCHA and auto-appending pages via \textit{ajax} calls. \small{[Solo~project]}}\\
    }{FarisHijazi/Rarbg-Enhancer-UserScript}
\smallskip \kern-1.2em \divider
}
