\cvsection{STUDENT ACTIVITIES}

\cvevent{Planning Committee Member (Chair)}{KFUPM Computer~Club}{2018 -- 2019}{Dhahran,Saudi~Arabia}
\verbose{
      Lead and presented courses such as ``Game~Development" and ``Python" short courses with over 50 attendees.
}{
      \begin{itemize}
            \item Lead and presented a ``Game~Development" short course with over 50 attendees.
            \item Managed, organized and presented in events and short-courses (Game~development, Intro~to~Python).
            \item Assigned tasks to members and distributed workload.
                  % \item Boosted team productivity and motivation.
            \item Took responsibility without blame, improvised and made spot decisions.
      \end{itemize}
}

\divider
\verbose{\small{
    \textbf{Leader of the KFUPM \href{https://www.robocup.org/}{RoboCup.org} team (embedded~systems)}.\ 
    \textbf{Major mentor \& guide} - advised younger students on career paths and presented summer training experience.\ 
    Represented the \textit{college~of~computer~sciene~and~engineering} at the \textbf{\href{https://www.scitech.sa}{SciTech.sa}} Expo,\ 
    \textbf{KFUPM volunteer} day 2016 ,\ 
    \textbf{Toastmasters club} %: started meetings, prepared rooms, maintained club property.
}
}{
    \begin{itemize}
          \item \textbf{Leader of the KFUPM \href{https://www.robocup.org/}{RoboCup.org} team (embedded~systems)}%
                \verbose{}{:Guided the team to constructing a moving robot with wireless communication within a single semester (3 months).}
          \item\textbf{Major mentor} - guided and advised orientation year students on career paths. Gave presentations on summer training experience and advised younger students.
          \item Represented the \textit{college~of~computer~sciene~and~engineering} at the \textbf{\href{https://www.scitech.sa}{SciTech.sa}} Expo\verbose{}{: presented to school students about computer majors, game development, and programming.}
          \item Participated in the \textbf{KFUPM volunteer} day 2016.
          \item \textbf{Toastmasters club} %: started meetings, prepared rooms, maintained club property.
    \end{itemize}
}
